\subsection{Capability Requirements}

	\subsubsection{Platform}\begin{enumerate}
		\item The application shall be compatible with the iOS mobile platform.
		\item The application shall be compatible with the Android mobile platform.
	\end{enumerate}
	
	\subsubsection{User Accounts}\begin{enumerate}
		\item If it is a user’s first-time opening the application, the application shall prompt the user to enter an email address, password, credit card information, and to create or link to a TAP account.
		\begin{enumerate}
			\item If the account is created successfully, the application shall send a confirmation to the user’s stored email address.
			\item If the account creation is not successful, the application shall display an error message that prompts the user to reenter their information and will not be logged in.
		\end{enumerate}
		\item If a returning user opens the application, it shall prompt the user to enter their log-in information.
			\begin{enumerate}
				\item If the log-in attempt fails, the application will display an error message that prompts the user to reenter their log-in information.
				\item If the log-in attempt succeeds, the user will be shown a transit management screen.
			\end{enumerate}
		\item The user shall be able to allow the application to automatically sign them in.
		\item The user shall be able to sign out of their account.
	\end{enumerate}
	
	\subsubsection{Usage}\begin{enumerate}
		\item If the application loses connectivity, the application shall display an error message.
		\item The application shall retrieve the user’s location at intervals of 120 $\pm$ 10 seconds.
		\item The application shall allow the user to manually refresh their location.
		\item Upon updating the user’s location, the application shall update information for nearby Metro transportation.
		\item The user shall be able to select which bus or train line is displayed first when the user is nearby a particular Metro station.
		\item The application shall allow the user to change their email address.
		\item The application shall allow the user to change their password.
		\item The application shall allow the user to delete their account.
		\item The user shall be able to link up to 5 dependents (name \& birthdate) to their account.
		\item The user shall be able to link up to 5 dependents TAP accounts to their account.
	\end{enumerate}
	
	\subsubsection{Payments}\begin{enumerate}
		\item The application shall allow users to purchase non-exclusive TAP passes.
		\item If the user selects to purchase a ticket, the application shall check to see if the user has an applicable TAP pass.
			\begin{enumerate}
				\item If the user has an applicable TAP pass, the application shall generate the selected virtual ticket.
				\item If the user does not have an applicable TAP pass, the application shall confirm with the user it will charge the stored credit card.
				\item If the card does not process, an error message shall be displayed and the order shall not be accepted. 
				\item If the transaction succeeds, the application shall create a virtual ticket. 
			\end{enumerate}
		\item If the user has more than one TAP unused pass, the application shall prompt the user to select which to use first.
		\item The user shall be able to select up to 2 dependents’ accounts to be attached to a virtual ticket.
			\begin{enumerate}
				\item If the dependent is over 5 years old, the application shall calculate the additional ticket fare.
			\end{enumerate}
		\item If the user selects to use their ticket, the application shall signal the gate up to a maximum of 3 attempts at 10 $\pm$ 5 second intervals to accept.
			\begin{enumerate}
				\item If the application is unsuccessful on the 3rd attempt, the application shall display an error message.
				\item Otherwise, the gate is unlocked, permitting the user to pass through.
			\end{enumerate}
		\item The application shall store unused virtual tickets for at least 1 year. 
		\item The application shall store used virtual tickets for at least 30 days.
		\item The application shall allow the user to change their credit card information.
		\item The user shall be able to set up the application to generate a default ticket that auto-charges their stored credit card when used.
		\item The application shall support remote adjustment of ticket prices (e.g., senior discount) by TAP id through a web interface.
		\item If the user has an active TAP pass, the application shall display how much time is remaining on the pass.
	\end{enumerate}		
\newpage	
\subsection{Level of Service Requirements}

\begin{table}[h]
    \begin{tabularx}{\textwidth}{Xrr}
    \hline
    LOS Requirements                                                                                          									& Desired Level & Accepted Level \\ \hline
    LOS-1: Concurrent Users														& $150000$		& $75000$           \\
    LOS-2: Start-up and user location time 										& 7 s  			& 15 s           \\
    LOS-3: Ticket Purchase Transaction Time										& 5 s 			& 20 s            \\
    LOS-4: Update Account Information Time										& 10 s 			& 30 s            \\
    LOS-5: Tickets stored per User												& 1500 			& 500            \\
    LOS-6: \% first-time users able to purchase ticket without outside help		& 80  			& 75             \\
    LOS-7: \% first-time users able to use ticket without outside help			& 85 			& 80             \\
    LOS-8: \% users that ride metro at least once per week that would rate 
    ease of use at 3 out of 5 or higher											& 90  			& 80             \\
    LOS-9: Average Time for User to Create an Account							& 45 s			& 60 s            \\
    LOS-10: Failed Ticket Purchases per 1000 									& 0.25  		& 1              \\
    LOS-11: Failed Ticket Uses per 1000  										& 0.25  		& 1              \\
    LOS-12: Hours per day that app shall purchase tickets 						& 20  			& 19.5             \\
    LOS-13: Hours per day that app shall allow use of tickets   				& 20 			& 19.5             \\
    LOS-14: \# iOS generations app shall support 								& 3  			& 2              \\
    LOS-15: \# Android generations app shall support   							& 3  			& 2              \\
    LOS-16: \# versions of app that Metro system shall support  				& 3    			& 2              \\
    \hline
    \end{tabularx}
\end{table}